\section{Introduction}

% Uni-core processor scaling over that past decade has stagnated due to increasing power consumption for marginal performance gains. Modern computing systems are seeing proliferation into multi-core and many-core processors. Parallel and shared memory applications are becoming increasingly important to fully utilize these current and upcoming architectures. However, the communication bandwidth between compute units is the main bottleneck for further boosts in performance. The key to future advancements lies within the communication infrastructure, ...

% Memory access misses private caches are either due to the cache line not being present or in the wrong coherence states. In a write-invalidate cache coherence protocol, a store operation to a local cache which misses for any reason would send invalidation requests to remote caches with the same cache line. Subsequent load or stores in the remote caches to that line would register a miss and generate corresponding coherence requests...

% A significant portion misses due to coherence related invalidation come from silent stores \cite{Lepak2002}, storing values that exactly match what is being overwitten. This suggest that there is a high degree of value locality \cite{Lipasti1996}. Existing work has examined squashing silent stores for reduce misses and improve performance \cite{Lepak2000, Lepak2002}. We however delve into the domain of approximate computing to expolit the intrinsic error-tolerance of certain applications to minimize coherence traffic with "acceptable" loss in application output quality. We do so by first introducting a novel workload characterization metric -- \textit{store-value similarity}. \textit{Store-value similarity} describes a probability distribution of the relative difference of a store value, and the value being overwritten in a memory location. It can be used to classify which applications would benefit from computing on approximate values to trade off output quality with a reduction in NoC traffic. Higher \textit{store-value similarity} corresponds to a higher probabilty of stores overwriting a memory location with values in a narrower range. Next we propose a coherence protocol optimization, Silent Approximate Stores (\textit{SAS}) tailored for error-tolerant, approximate applications to reduce coherence traffic by exploiting stores with high \textit{store-value similarity}. The protocol implements \textit{approximate stores}, where if the relative difference between a store value and what is being overwritten is within a programmer defined tolerance, the store is completed maintaining the lines current coherence state. This minimizes coherence traffic by inhibiting invalidations to remote caches which in turn reduces the amount of misses on subsequent accesses to invalidated lines.


Uni-core processor scaling over that past decade has stagnated due to increasing power consumption for marginal performance gains. Modern computing systems are seeing proliferation into multi-core and many-core processors, thus parallel and shared memory applications are becoming increasingly important to fully utilize these current and upcoming architectures. However, the communication infrastructure and bandwidth between compute units is the main bottleneck for further improvements. This infrastructure, namely the cache coherence protocol, maintains correctness of shared memory between private caches. Although the data is kept coherent throught execution of an application, it can lead to communication inefficiencies when multiple writers access the same data (true-sharing), or data that is not logically shared but resides on the same cache line (false-sharing). This causes data to be passed back and forth between nodes which inflicts additional latency, energy, and scalability issues.

As many application domains are inherently error-tolerant (e.g., machine learning, multimedia, scientific applications), we can leaverage the approximate computing domain to trade-off precise data integrity for greater performance and energy-efficiency. We propose a coherence protocol modification, Lossy Coherence, which is built on top of existing protocols to relax the correctness of shared data values within approximate applications. Lossy Coherence  introduces an approximate store instruction (\storea) to write data to the cache lines in coherence states where a conventional store would result in a miss. The \storea instructions minimize coherence transactions for true-sharing and false-sharing at a cost of making data values incoherent between caches. We show that for several approximate applications, we gain considerable energy reduction and speedup with acceptable accuracy loss for different levels of approximation.